IPv6 over Low-Power Wireless Personal Area Networks\\ MSc. Thesis Proposal

### 2009-12-19 trunk/doc/msc-proposal/msc-routing.tex
proposal: ND

\chapter{6LoWPAN Routing}\label{ch:routing}
Neither the IEEE 802.15.4 \cite{ieee802.15.4} standard nor the 6LoWPAN format specification \cite{rfc4944} define how mesh topologies could be obtained and maintained. In 6LoWPAN routing can be perforem either in the IP-layer, using a Route Over approach, or in the adaptation layer described in Section \ref{subsec:mesh.header}, using the Mesh Under approach.

>>>>

\chapter{6LoWPAN Routing}\label{ch:routing}
Neither the IEEE 802.15.4 \cite{ieee802.15.4} standard nor the 6LoWPAN format specification \cite{rfc4944} define how mesh topologies could be obtained and maintained. In 6LoWPAN routing can be performed either in the IP-layer, using a route over approach, or in the adaptation layer, described in Section \ref{subsec:mesh.header}, using the mesh under approach. The mesh under approach performs the multi-hop communication below the IP link and therefore a 6LoWPAN is seen as a single IP link.

A 6LoWPAN network comprises nodes which are either hosts or routers. A host is a node that only sources or sinks IPv6 datagrams, whereas a router forwards datagrams between arbitrary source-destination pairs. Routers are present only in a route over configuration, where the network is composed of overlapping link-local scopes, to overcome non-transitive nature of links.
